\subsection{Login}
The visitor landing on myTaxiService site or app has the possibility to provide username (or email) and password to access the service, if he/she is already registered to the service. Submitted wrong informations will be notified by the system to the visitor. User who doesn't remember him/her login informations can ask the system to provide him/her the username and a new password. The visitor not registered can reach registration page.

\paragraph{Scenarios}
\begin{enumerate}
	\item Alan opens myTaxiService mobile app. He is not registered to the service indeed he wants to. He taps on "Register" in the bottom of screen. Now, providing his personal informations, he can register to the service.
	\item Berry is a new user. He opens myTaxiService website but doesn't remember his password to access the service so he clicks on "Forgotten username and password?". He has to insert the mail provided at registration and if it is correct the system will send the username and a new password to the email.
	\item Charlie is familiar with myTaxiService website and he wants to use also the mobile app. He knows that he can enter either username or email and password. He clicks on Login. It is successful.
\end{enumerate}

\subsection{Registration}
The visitor, from the home page of the service both web or mobile application, can reach the registration page. The user can choose between two kinds of registration, one as a passenger the other as a taxi driver. Both registrations require providing personal informations but the latter needs more data and a valid taxi license. After the visitor agrees to Terms of use, Privacy policy, and License Agreement, and his/her informations verified, he/she receives a confirmation email. The visitor, after the confirmation of email, is able to use the service.

\paragraph{Scenarios}
\begin{enumerate}
	\item Daisy is a taxi driver. myTaxiService has been just released. She wants to subscribe the service so she reaches the web site. She provides all her personal informations and her taxi license credentials. The system verifies her informations and sends her an email confirmation. She confirms her mail. Now Daisy is registered to the service as a taxi driver but she has to use her mobile application to be able to use the service. She downloads the application on his phone and, if it is provided with a GPS navigation system, use the service.
	\item Ellie hasn't got a car but she has to commute to work. She opens the application on her phone and taps on "Register". She provides her personal information.........
\end{enumerate}
\subsection{Ride request}