\subsection{Regulatory policies}
myTaxiService is a service provided by the public company \textbf{ATM} responsible for public transportation in \textbf{Milan} city. The user, who reaches this service by web or mobile application, has to agree to License Agreement rather than Privacy policy and Terms of use at registration.

The user access and use of the services constitutes his/her agreement to be bound by these Terms, which establishes a contractual relationship between him/her and myTaxiService. If user does not agree to these Terms, he/she may not access or use the services. myTaxiService may immediately terminate these Terms or any services with respect to him/her, or generally cease offering or deny access to the Services or any portion thereof, at any time for any reason.

myTaxiService collects the information provided by the user, for example when creating or making changes to services on demand, through contact with customer service or during other communications. This information may include: name, email, phone number, mailing address, profile picture, payment method, products required (for service delivery), delivery receipts and other information user choose to provide. The personal data will be used only to provide the services requested.

User is responsible for obtaining the data network access necessary to use the services. User mobile network's data and messaging rates and fees may apply if he/she accesses or uses the services from a wireless-enabled device. User is responsible for acquiring and updating compatible hardware or devices necessary to access and use the service and applications and any updates thereto. myTaxiService does not guarantee that the services, or any portion thereof, will function on any particular hardware or devices. In addition, the services may be subject to malfunctions and delays inherent in the use of the Internet and electronic communications.

\subsection{Hardware limitations}
myTaxiService defines the minimum requirements for using web and mobile applications.
\begin{itemize}
\item \emph{Web application}\\
Supported browsers: Chrome, Internet Explorer, Firefox, Safari. Other browsers may also work\\
Web access at the minimum speed of 1Mbps
\item \emph{Mobile application}\\
Operating system: Android, iOS, Windows Phone\\
Memory: 512MB RAM\\
Hard drive: 50MB of free space\\
GPS navigation system (only for taxi drivers)\\
Web access at the minimum speed of 1Mbps
\end{itemize}

\subsection{Interfaces to other applications}
%TODO
myTaxiService does not have to meet any interface to other applications.

\subsection{Parallel operation}
%TODO
myTaxiService supports parallel operations cause of the nature of service. Many users can access to the service at same time thus system and database have to work with parallel requests.

\subsection{Reliability requirements}
%TODO

\subsection{Criticality of the application}
%TODO 

\subsection{Safety and security considerations}
%TODO