\begin{enumerate}
	\item \textbf{Visitors can register either as passengers or as taxi drivers}\\
	Account manager receives user registrations from web or mobile applications through Account API. User informations are stored by myTaxiDatabase through Data API of Data Manager.

	\item \textbf{Visitors can abort the registration process at any time.}\\
	Account manager does not consider unfulfilled registrations. No data is stored.
	
	\item \textbf{The link in the confirmation email must be clicked within 1 day, otherwise the registration is deleted along with the visitor's info.}\\
	Account manager takes care of sending the confirmation email to new user. User informations will be deleted from myTaxiDatabase if the registration has not been confirmed.
	
	\item \textbf{Registration form requires user's info (fields). All fields must be contain valid inputs (see RASD for further informations)}\\
	Account manager does not consider unfulfilled registrations.	
	
	\item \textbf{Email address and username cannot be the same as ones from other myTaxiService users}\\
	Account manager ensures the uniqueness of users.
	
	\item \textbf{Password must contain at least 8 characters}\\
	Validation is made by client apps. Further controls are made by Account manager.
	
	\item \textbf{Password and password confirmation must match.}\\
	Two times password providing is requested by client apps to prevent typos.
	
	\item \textbf{Visitors can log in either as passengers or as taxi drivers}\\
	Account manager allows access to service only to registered user.
	
	\item \textbf{Visitors must fill the "username" field either with an existing username or with an existing email address in order to successfully log in}\\
	Account manager accepts either username or email in order to login.
	
	\item \textbf{Visitors must fill the "password" field with the only password corresponding to the submitted username/email address in order to successfully login}\\
	Account manager checks the submitted password with the one associated with user.
	
	\item \textbf{The system will ignore log in requests if at least one of the "username" and "password" fields are left blank}\\
	Blank fields let the client app to ignore the login.	
	
	\item \textbf{The system allows visitors to retrieve their password if they forget it, by clicking "Forgot password?"}\\
	Client apps provide this functionality. Account manager will take care of the recovery procedure.
	
	\item \textbf{The system requires visitors to submit an existing email address in the "username" field in order to retrieve their password}\\
	To recover a password client apps require the email associated with the user.
	
	\item \textbf{The system will take care of assigning the user a new password, when he/she states to have lost the previous one}\\
	Account manager generates a new password that will replace the older one. 
	
	\item \textbf{The system will take care of sending to the email address submitted by the visitor the new assigned password, when he/she states to have lost the previous one}\\
	Account manager sends a mail to the user with the new password.
	
	\item \textbf{The system allows visitors to retrieve their password once a day}\\
	Account manager permits a password recovery once a day.
	
	\item \textbf{The system allows standard taxi ride requests to passenger users}\\
	Client apps allow the user to request a standard ride. Further control will be made by Ride manager during ride request procedure.
	
	\item \textbf{The system allows standard taxi ride requests both on the web and on the mobile application}\\
	Standard ride requests are allowed from either web or mobile applications.
	
	\item \textbf{The system allows taxi ride requests if and only if the passenger accepts to give info about his/her location, either through GPS or directly writing down a valid location}\\
	Client apps check if a location from GPS or input is valid. This is made by implementing Google Maps API.
	
	\item \textbf{The system allows taxi ride requests if and only if the passenger can be located in some definite position of some definite taxi zone}\\
	Ride manager checks, through Map services, if a position is in a definite tazi zone.
	
	\item \textbf{The system uses default values for the number of passengers and sharing preferences of a ride (1 person, no sharing), unless the passenger does specify them}\\
	Client apps let that if a preference for a ride request is untouched, default value is used.
	
	\item \textbf{The system uses a FIFO policy to manage forwarding of pending ride requests}\\
	Ride manager handles forwarding of pending ride requests through a FIFO policy.
	
	\item \textbf{The system uses a FIFO policy to manage the order of taxi drivers in queues to send notifications to}\\
	Taxi queues handles the order of taxi drivers through a FIFO policy.
	
	\item \textbf{The system forwards a ride request to the first taxi driver in the considered	zone queue if and only if he/she has a sufficient number of free seats available in his/her vehicle}\\
	Ride manager finds the first available cab with the corresponding number of free seats from queues provided by Taxi queues.
	
	\item \textbf{The system keeps the passenger(s) notified about the status of the ride request he/she sent}\\
	Notification component keeps the passenger up-to-date by requests from Ride manager.
	
	\item \textbf{Once a ride request has been accepted by some taxi driver, the system changes the request status from "Pending" to "Accepted"}\\
	Ride request ensures the passenger to be updated about the ride status by Notification component.
	
	\item \textbf{Once a ride request has been accepted by some taxi driver, the system calculates the ETA of the incoming taxi based on the distance between the taxi and the passenger(s), and the current traffic}\\
	Ride manager asks Map services to calculate the ETA.
	
	\item \textbf{Once a ride request has been accepted by some taxi driver, the system notifies the passenger(s) about the ETA of the incoming taxi}\\
	Ride manager asks Notification to send ETA to the passenger.
	
	\item \textbf{Once a ride request has been accepted by some taxi driver, the system keeps the passenger(s) notified about the current location of the incoming taxi, showing its position on a map}\\
	Ride manager keeps the passenger updated about taxi driver current position through Map services and Notification.
	
	\item \textbf{Once a ride request has been accepted by some taxi driver, the system prevents the passenger(s) to make a new ride request until the taxi driver changes the status of the ride to "Completed"}\\
	Client apps prevent user from making new requests if there's a pending one. 
	
	\item \textbf{The system allows reserved taxi ride requests to passenger users}\\
	Client apps allow user to request a reserved ride.
	
	\item \textbf{The system allows reserved taxi ride requests both on the web and on the mobile application}\\
	Reserved ride requests are allowed from either web or mobile applications.
	
	\item \textbf{The system allows reserved taxi ride requests if and only if the passenger gives definite existing positions of some definite existing taxi zones both for "Origin" and "Destination" fields}\\
	Client apps check if a location from GPS or input is valid. This is made by implementing Google Maps API.
	
	\item \textbf{The system allows passengers to select locations either through GPS or directly writing down a valid location}\\
	Client apps allow user to select location either through GPS or user input.
	
	\item \textbf{The system allows reserved taxi ride requests if and only if the passenger gives complete info about the date and the time of the meeting}\\
	Client apps check if date and time informations are valid.
	
	\item \textbf{The system allows reserved taxi ride requests if and only if the time of the request occurs at least two hours before the ride meeting time}\\
	Client apps check if a reserved ride is scheduled two hours later from request.
	
	\item \textbf{The system forwards notifications to taxi drivers about reserved taxi ride requests 10 minutes before the ride meeting time}\\
	Ride manager ensures that a taxi driver is informed 10 minutes before the reserved ride.
	
	\item \textbf{The system allows taxi ride sharing to passenger users}\\
	Client apps allow user to request a shared ride.
	
	\item \textbf{The system allows taxi ride sharing both on the web and on the mobile application}\\
	Shared ride requests are allowed from either web or mobile applications.
	
	\item \textbf{The system allows both standard shared taxi ride requests and reserved shared taxi ride requests, simply ticking the "Share" checkbox while doing any kind of taxi ride request}\\
	Client apps allow standard and reserved ride request to be shared.
	
	\item \textbf{Both kinds of shared ride requests require no less data than their non-shared forms (see "Standard ride request" and "Reserved ride request")}\\
	Client apps ensure the completeness of informations for ride requests.
	
	\item \textbf{The system allows standard shared taxi ride requests if and only if the passenger also gives a definite existing position of some definite existing taxi zone as "Destination" (reserved taxi ride requests already require this, even if non-shared)}\\
	Client apps check if a location from GPS or input is valid. This is made by implementing Google Maps API.
	
	\item \textbf{The system allows passengers to select the input for "Destination" either through GPS or directly writing down a valid location}\\
	Client apps allow user to select location either through GPS or user input.	
	
	\item \textbf{The system, at the time of forwarding any shared ride request, will use a specific algorithm to calculate good arrangements between different shared ride requests}\\
	Ride manager calculates good arrangements for shared request.
	
	\item \textbf{The arrangement algorithm search different shared ride requests to form a single, grouped, shared ride request}\\
	Ride manager searches different shared ride requests to form a single, grouped, shared ride request. 
	
	\item \textbf{The arrangement algorithm considers for grouping only shared rides with close "Origin" positions and similar directions towards "Destination" positions. Similar directions means that going from the origin to the farthest destination implies passing by the other destination(s) as well}\\
	Ride manager uses Map services and Taxi queues components to take advantage of the algorithm. 
	
	\item \textbf{The arrangement algorithm also considers the total number of passengers in a taxi. Groups that would occupy too many seats are not eligible}\\
	Ride manager considers total number of passengers in a taxi.
	
	\item \textbf{The arrangement algorithm can group even standard and reserved ride requests together, as long as all the others requirements are met}\\
	Ride manager can group different types of ride requests. 
	
	\item \textbf{The arrangement algorithm may take up to 1 minute to wait the reception of new shared ride requests that satisfy the grouping requirements}
	Ride manager may take up to 1 minute to wait the reception of new shared ride requests.
		
	\item \textbf{The system will consider group requests as a single one when forwarding them to taxi drivers}\\
	Ride manager forwards a single request for grouped requests.
	
	\item \textbf{Taxi drivers can see all details of all shared requests when receiving notification of a grouped request}\\
	Ride manager takes care of informing taxi driver of all details of a grouped request. Notification will dispatch the message.
	
	\item \textbf{Taxi drivers can accept or refuse grouped requests as normal}\\
	Mobile app allows a taxi driver to accept or refuse a grouped request.
	
	\item \textbf{The system will automatically split up groups of shared requests if they're continuously refused, or simply not accepted, for 3 minutes since their forwarding}\\
	Ride manager splits up a grouped request if it is continuously refused.  
	
	\item \textbf{The system will then proceed to recalculate possible groups with the special algorithm, but excluding the arrangements that were already tried}\\
	Ride manager tries different combinations of groups.
	
	\item \textbf{The system calculates how to split taxi fees equally on all passengers on a shared ride, depending on the distance travelled by each one and the number of passengers during each part of the ride}\\
	Ride manager calculates how to split taxi fees equally among passengers in a grouped ride request.
	
	\item \textbf{The system notifies the taxi driver how much of the total fee each passenger will have to pay, in percentage}\\
	Ride manager notifies the taxi driver of fees' percentages through Notification component.
	
	\item \textbf{The system allows taxi drivers to receive ride request notifications on their mobile phone application and respond to them, either accepting or refusing}\\
	Mobile app allows taxi driver to receive ride requests and respond to them.
	
	\item \textbf{The system notifies taxi drivers about all request notifications forwarded to them}\\
	Notification component takes care of all messages from service to taxi drivers.
	
	\item \textbf{Taxi zone queues contain only taxi drivers that currently have status "Ready"}\\
	Taxi queues component handles taxi driver that have "Ready" status through Account manager.
	
	\item \textbf{Taxi zone queues contain only taxi drivers that are currently located in that taxi zone}\\
	Taxi queues component manages a city zone queue with taxi drivers located in that city zone.
	
	\item \textbf{Taxi ride notifications show all requesting passengers' username and position on a map}\\
	Taxi drivers are able to see on mobile app all requesting passengers.
	
	\item \textbf{The system gives taxi drivers one minute to accept or refuse request notifications, otherwise take it as a refusal. This is to avoid long waiting times for passengers}\\
	Ride manager gives to taxi drivers a window of one minute to accept or refuse a ride request.
	
	\item \textbf{Once a ride request has been accepted by some taxi driver, the system changes his/her status to "Busy" and he/she's removed from his/her taxi zone queue}\\
	Account manager takes care of changing taxi driver status from "Ready" to "Busy" when he/she accepts a ride request. Taxi queues component will remove him/her from queues.
	
	\item \textbf{The system allows taxi drivers to notify the end of the ride, when they're doing one (i.e. when they accepted a ride request)}\\
	Mobile application allows taxi drivers to notify the end of ride to the system.
	
	\item \textbf{Once a taxi driver notifies the end of a ride, the system changes his/her status to "Ready" and he/she's put on the bottom of his/her taxi zone queue}\\
	Account manager takes care of changing taxi driver status from "Busy" to "Ready" when he/she ends a ride. Taxi queues component will add him/her to queues.
	
	\item \textbf{The system uses info provided by the GPS to locate taxis and decide their respective queues}\\
	Location data provided by mobile application are used by Ride manager and Taxi queues components for queues managing.
	
	\item \textbf{The system automatically inserts taxi drivers in queues when their status changes to "Ready"}\\
	Taxi queues adds a taxi driver to a queue if he/she changes him/her status to "Ready".
	
	\item \textbf{The system automatically removes taxi drivers from queues when their status changes to "Busy" or "Offline"}\\
	Taxi queues removes a taxi driver from a queue if he/she changes his/her status to "Busy" or "Offline".
	
	\item \textbf{The status automatically changes to "Busy" when the taxi driver accepts a ride request}\\
	Ride manager changes a taxi driver status to "Busy" when the taxi driver accepts a ride request.
	
	\item \textbf{The status automatically changes to "Ready" when the taxi driver notifies the end of a ride}\\
	Ride manager changes a taxi driver status to "Ready" when the taxi driver ends a ride.
	
	\item \textbf{When status is "Ready", the application notifies about ride requests}\\
	Ride manager notifies taxi drivers, through Notification component, about ride requests.
	
	\item \textbf{When status is "Ready", the application enables the taxi driver to accept/refuse requests}\\
	Mobile app allows taxi drivers to accept/refuse a request if his/her status is "Ready".
	
	\item \textbf{When status is "Busy", the application prevents ride requests notifications}\\
	Ride manager does not notify taxi drivesr, through Notification component, about ride requests.
	
	\item \textbf{When status is "Busy", the application enables the taxi driver to notify the end of the current ride}\\
	Mobile app allows taxi drivers to notify the end of a ride if his/her status is "Busy".
	
	\item \textbf{Account settings are available to both passenger and taxi driver users}\\
	Account manager allows users to access to their profile informations.
	
	\item \textbf{Account settings are available both on the web and the mobile application}\\
	Account settings are allowed from either web or mobile applications.
	
	\item \textbf{Account settings are accessible from the start screen of both apps, through the "Profile" button}\\
	Client apps allow users to access account settings.
	
	\item \textbf{The system allows users to view all their profile info, submitted during registration}\\
	Client apps allow users to view all their personal informations.
	
	\item \textbf{The system allows users to modify all their profile info, submitted during registration, with the only exception of username}\\
	Account manger allows users to edit personal informations with the only exception of username.
	
	\item \textbf{Modifying the password requires to write the old one, and the new one twice; if the former password is not correct or if the two new passwords submitted do not match, the system asks for all passwords again and notifies the user}\\
	Account manager allows users to change their passwords.
	
	\item \textbf{Modifying the email address, the taxi license ID or the taxi code requires that the new one doesn't match with the one of another registered user}\\
	Account manager ensures the uniqueness of email address, taxi license ID and taxi code.
	
	\item \textbf{ Modifying the email address requires confirmation through an email sent to the submitted email address}\\
	Account manager requires email confirmation after a change of it.
	
	\item \textbf{The system allows users to abort modifications at any time}\\
	Client apps allow users to abort profile editing.
	
	\item \textbf{The system allows users to delete their account: confirmation is required	to proceed}\\
	Account manager allows users to delete their accounts. Client apps provide this functionality and ask for a confirmation during this process.	
\end{enumerate}